Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd

With the purpose of identifying influential variables impacting blood
pressure, a variable selection process was conducted. The initial
approach involved employing best subset selection with 10-fold
cross-validation to ascertain the optimal number of subsets. Notably,
for systolic blood pressure, the forward best subset selection method
discerned 13 variables, whereas diastolic blood pressure exhibited 19
selected variables. However, a limitation inherent in forward best
subset selection is its inability to eliminate previously selected
features, potentially disregarding their relevance in light of newly
added variables. Consequently, this methodology may yield sub-optimal
variable selections due to its lack of adaptability.

In an effort to mitigate this limitation and introduce regularization,
LASSO regularization was employed. This involved a 10-fold
cross-validation process to determine the optimal penalty parameter,
$\lambda$ . For diastolic blood pressure, the $\lambda$ value associated
with the lowest mean squared error (MSE) led to the selection of 25
variables. Conversely, when considering systolic blood pressure, the
$\lambda$ value minimizing the MSE resulted in the exclusion of a sole
variable. Subsequently, a $\lambda$ value was strategically chosen to
ensure a negligible increase of no more than 1% in MSE, ultimately
leading to the inclusion of 29 variables in the model.

>>>>

Furthermore, we conducted two distinct variable selection methodologies,
similarly excluding hypertension. Model 6 was based on best subset
selection with 10-fold cross-validation to ascertain the optimal number
of subsets. Notably, for systolic blood pressure, the forward best
subset selection method discerned 13 variables, whereas diastolic blood
pressure exhibited 19 selected variables. However, a limitation inherent
in forward best subset selection is its inability to eliminate
previously selected features, potentially disregarding their relevance
in light of newly added variables. Consequently, this methodology may
yield sub-optimal variable selections due to its lack of adaptability.

In an effort to mitigate this limitation and introduce regularization,
LASSO regularization was employed. This involved a 10-fold
cross-validation process to determine the optimal penalty parameter,
$\lambda$ . For diastolic blood pressure, the $\lambda$ value associated
with the lowest mean squared error (MSE) led to the selection of 25
variables. Conversely, when considering systolic blood pressure, the
$\lambda$ value minimizing the MSE resulted in the exclusion of a sole
variable. Subsequently, a $\lambda$ value was strategically chosen to
ensure a negligible increase of no more than 1% in MSE, ultimately
leading to the inclusion of 29 variables in the model. Model 7 consisted
in variables selected by the LASSO regression. In addition, our study
incorporated an alternative model that not only incorporated the
variables identified through LASSO but also introduced an interaction
term involving age and cholesterol levels; Model 8. This extended model
aimed to explore potential combined effects between age and cholesterol
on the outcome variable.
